\pkg{systemfit}: A Package for Estimating Systems of Simultaneous Equations in \proglang{R}

### 2008-09-12 paper/trunk/systemfit.Rnw
the master file (systemfit.tex) is an Sweave file now (systemfit.Rnw) (although it not yet contains R code but the subfiles should be moved into this master file soon)
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@947 591db2bd-e0a0-4d22-8c19-2192dbb7da31

\hyphenation{sys-tem-fit}

\author{Arne Henningsen\\University of Kiel\And
        Jeff D. Hamann\\ Forest Informatics, Inc. }

\title{\pkg{systemfit}: A Package for Estimating\\
       Systems of Simultaneous Equations in \proglang{R}}

%% for pretty printing and a nice hypersummary also set:
\Plainauthor{Arne Henningsen, Jeff D.\ Hamann} %% comma-separated
\Plaintitle{systemfit: A Package for Estimating Systems of Simultaneous Equations
            in R} %% without formatting
\Shorttitle{\pkg{systemfit}: A Package for Estimating
   Systems of Simultaneous Equations in \proglang{R}}
   %% a short title (if necessary)

@@

%% publication information
%% NOTE: This needs to filled out ONLY IF THE PAPER WAS ACCEPTED.
%% If it was not (yet) accepted, leave them commented.
%% \Volume{13}
%% \Issue{9}
%% \Month{September}
%% \Year{2006}
%% \Submitdate{2006-02-28}
%% \Acceptdate{2006-09-29}

%% The address of (at least) one author should be given
%% in the following format:
\Address{
   Arne Henningsen\\
   Department of Agricultural Economics\\
   University of Kiel\\
   D-24098 Kiel, Germany\\
   E-mail: \email{ahenningsen@agric-econ.uni-kiel.de}\\
   URL: \url{http://www.uni-kiel.de/agrarpol/ahenningsen/}\\
   \\
   Jeff D.\ Hamann\\
   Forest Informatics, Inc.\\
   PO Box 1421\\
   Corvallis, Oregon 97339-1421\\
   e-mail: \email{jeff.hamann@forestinformatics.com}\\
   URL: \url{http://www.forestinformatics.com}\\
}
%% It is also possible to add a telephone and fax number
%% before the e-mail in the following format:
%% Telephone: +43/1/31336-5053
%% Fax: +43/1/31336-734

@@

\appendix
\input{systemfit_compare_lm.tex}

@@

>>>>

\hyphenation{systemfit}

\author{Arne Henningsen\\University of Kiel
   \And Jeff D.\ Hamann\\ Forest Informatics, Inc.}
\Plainauthor{Arne Henningsen, Jeff D. Hamann}

\title{\pkg{systemfit}: A Package for Estimating Systems of Simultaneous Equations in \proglang{R}}
\Plaintitle{systemfit: A Package for Estimating Systems of Simultaneous Equations in R}
\Shorttitle{\pkg{systemfit}: Estimating Systems of Simultaneous Equations in \proglang{R}}

@@

%% publication information
%% NOTE: This needs to filled out ONLY IF THE PAPER WAS ACCEPTED.
%% If it was not (yet) accepted, leave them commented.
\Volume{23}
\Issue{4}
\Month{December}
\Year{2007}
\Submitdate{2006-03-15}
\Acceptdate{2007-10-24}

%% The address of (at least) one author should be given
%% in the following format:
\Address{
   Arne Henningsen\\
   Department of Agricultural Economics\\
   University of Kiel\\
   D-24098 Kiel, Germany\\
   E-mail: \email{ahenningsen@agric-econ.uni-kiel.de}\\
   URL: \url{http://www.uni-kiel.de/agrarpol/ahenningsen/}\\
   \\
   Jeff D.\ Hamann\\
   Forest Informatics, Inc.\\
   PO Box 1421\\
   Corvallis, Oregon 97339-1421, United States of America\\
   E-mail: \email{jeff.hamann@forestinformatics.com}\\
   URL: \url{http://www.forestinformatics.com/}\\
}
%% It is also possible to add a telephone and fax number
%% before the e-mail in the following format:
%% Telephone: +43/1/31336-5053
%% Fax: +43/1/31336-734

@@

\clearpage

\begin{appendix}

\input{systemfit_compare_lm.tex}

@@

\end{appendix}
